peter_models

### 2024-12-08 peter_models.qmd
updating with brant test

@@

predict(m_mult, new_dataset, type = "probs")
```

>>>>

# Testing proportional odds assumption with Brant test
```{r}
library(brant)
brant(ord_mod_interactions)
```

@@

predict(m_mult, new_dataset, type = "probs")
```
# Comparing confusion matrix
```{r}
# Confusion matrix for ordinal model with interactions
confusionMatrix(predict(ord_mod_interactions), dataset_clean$Q29, mode="everything")

# Confusion matrix for multinomial model
conf_matrix
```
